### 2023-03-02 resources/interventions.tex
manuscript prepared

% Created by tikzDevice version 0.12.3.1 on 2022-06-28 15:57:56
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

@@

\end{document}
re}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (469.75,216.81);
\begin{scope}
\path[clip] ( 25.15, 47.51) rectangle (167.85,198.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.15, 47.51) rectangle (167.85,198.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 31.63, 54.37) rectangle ( 68.70,164.08);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 77.97, 54.37) rectangle (115.03,122.94);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (124.30, 54.37) rectangle (161.36, 68.09);
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 31.63,164.08) rectangle ( 68.70,191.51);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 77.97,122.94) rectangle (115.03,191.51);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (124.30, 68.09) rectangle (161.36, 81.80);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (  3.83, 54.37) rectangle (  3.83, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 25.15, 88.66) -- (167.85, 88.66);
\end{scope}
\begin{scope}
\path[clip] (173.35, 47.51) rectangle (316.05,198.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (173.35, 47.51) rectangle (316.05,198.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (179.84, 54.37) rectangle (216.90, 88.66);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (226.17, 54.37) rectangle (263.23, 88.66);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (272.50, 54.37) rectangle (309.57, 68.09);
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (179.84, 88.66) rectangle (216.90,116.08);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (226.17, 88.66) rectangle (263.23,157.22);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (272.50, 68.09) rectangle (309.57, 81.80);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (152.04, 54.37) rectangle (152.04, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (173.35, 88.66) -- (316.05, 88.66);
\end{scope}
\begin{scope}
\path[clip] (321.55, 47.51) rectangle (464.26,198.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (321.55, 47.51) rectangle (464.25,198.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (328.04, 54.37) rectangle (365.10, 61.23);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (374.37, 54.37) rectangle (411.44, 54.37);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (420.70, 54.37) rectangle (457.77, 68.09);
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (328.04, 61.23) rectangle (365.10, 88.66);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (374.37, 54.37) rectangle (411.44,122.94);

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (420.70, 68.09) rectangle (457.77, 81.80);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] (300.24, 54.37) rectangle (300.24, 54.37);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (321.55, 88.66) -- (464.26, 88.66);
\end{scope}
\begin{scope}
\path[clip] ( 25.15,198.36) rectangle (167.85,211.31);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] ( 25.15,198.36) rectangle (167.85,211.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 27.65,201.74) {A) No intervention};
\end{scope}
\begin{scope}
\path[clip] (173.35,198.36) rectangle (316.05,211.31);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] (173.35,198.36) rectangle (316.05,211.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (175.85,201.74) {B) Static intervention};
\end{scope}
\begin{scope}
\path[clip] (321.55,198.36) rectangle (464.26,211.31);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] (321.55,198.36) rectangle (464.25,211.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (324.05,201.74) {C) Dynamic intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 50.17, 37.06) {p-yr 1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.50, 37.06) {p-yr 2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.83, 37.06) {p-yr 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (198.37, 37.06) {p-yr 1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (244.70, 37.06) {p-yr 2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (291.03, 37.06) {p-yr 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (346.57, 37.06) {p-yr 1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (392.90, 37.06) {p-yr 2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (439.24, 37.06) {p-yr 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 47.51) --
	( 25.15,198.36);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 51.62) {0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 54.37) --
	( 25.15, 54.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 88.66) --
	( 25.15, 88.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,122.94) --
	( 25.15,122.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,157.22) --
	( 25.15,157.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,191.51) --
	( 25.15,191.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,122.94) {Average annual exposure (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 49.28,  5.50) rectangle (189.07, 24.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 60.28, 11.00) rectangle ( 68.28, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line cap=rect,fill=fillColor] ( 60.99, 11.71) rectangle ( 67.56, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 73.78, 11.90) {Hypothetical exposure limit};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (200.07,  5.50) rectangle (440.13, 24.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (211.07, 11.00) rectangle (219.07, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (211.79, 11.71) rectangle (218.36, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (211.79, 11.71) rectangle (218.36, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (334.17, 11.00) rectangle (342.17, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (334.88, 11.71) rectangle (341.46, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (334.88, 11.71) rectangle (341.46, 18.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (224.57, 11.90) {Exposure to soluble MWF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (347.67, 11.90) {Other MWF  exposure};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2023-02-02 14:54:25
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}[Extension = .ttf,
			UprightFont = *,
			BoldFont = *bd,
			talicFont = *i,
			BoldItalicFont = *bi]

@@

\end{document}
ill opacity=0.00] (0,0) rectangle (361.35,216.81);
\begin{scope}
\path[clip] ( 25.15, 45.51) rectangle (187.75,198.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.15, 45.51) rectangle (187.75,198.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 32.54, 52.46) rectangle ( 74.77,163.62);

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 85.33, 52.46) rectangle (127.56,121.94);

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (138.12, 52.46) rectangle (180.36, 66.36);
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 32.54,163.62) rectangle ( 74.77,191.41);

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 85.33,121.94) rectangle (127.56,191.41);

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (138.12, 66.36) rectangle (180.36, 80.25);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (  0.86, 52.46) rectangle (  0.86, 52.46);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (  0.86, 52.46) rectangle (  0.86, 52.46);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (  0.86, 52.46) rectangle (  0.86, 52.46);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 25.15, 87.20) -- (187.75, 87.20);
\end{scope}
\begin{scope}
\path[clip] (193.25, 45.51) rectangle (355.85,198.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (193.25, 45.51) rectangle (355.85,198.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (200.64, 52.46) rectangle (242.87, 87.20);

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (253.43, 52.46) rectangle (295.67, 87.20);

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (306.22, 52.46) rectangle (348.46, 66.36);
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (200.64, 87.20) rectangle (242.87,114.99);

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (253.43, 87.20) rectangle (295.67,156.68);

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (306.22, 66.36) rectangle (348.46, 80.25);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (168.96, 52.46) rectangle (168.96, 52.46);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (168.96, 52.46) rectangle (168.96, 52.46);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (168.96, 52.46) rectangle (168.96, 52.46);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (193.25, 87.20) -- (355.85, 87.20);
\end{scope}
\begin{scope}
\path[clip] ( 25.15,198.36) rectangle (187.75,211.31);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] ( 25.15,198.36) rectangle (187.75,211.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 27.65,201.74) {A) No intervention};
\end{scope}
\begin{scope}
\path[clip] (193.25,198.36) rectangle (355.85,211.31);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round,fill=fillColor] (193.25,198.36) rectangle (355.85,211.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (195.75,201.74) {B) Intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 53.66, 35.06) {p-yr 1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.45, 35.06) {p-yr 2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (159.24, 35.06) {p-yr 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (221.76, 35.06) {p-yr 1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (274.55, 35.06) {p-yr 2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (327.34, 35.06) {p-yr 3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 45.51) --
	( 25.15,198.36);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 20.20, 49.71) {0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 52.46) --
	( 25.15, 52.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40, 87.20) --
	( 25.15, 87.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,121.94) --
	( 25.15,121.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,156.68) --
	( 25.15,156.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 22.40,191.41) --
	( 25.15,191.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,121.94) {Average annual exposure (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 75.97, 19.50) rectangle (305.02, 22.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 81.47, 19.50) rectangle ( 89.47, 27.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 82.18, 20.21) rectangle ( 88.76, 26.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] ( 82.18, 20.21) rectangle ( 88.76, 26.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (204.57, 19.50) rectangle (212.57, 27.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (205.28, 20.21) rectangle (211.86, 26.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{211,211,211}

\path[draw=drawColor,line width= 0.6pt,fill=fillColor] (205.28, 20.21) rectangle (211.86, 26.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 94.97, 20.40) {Exposure to soluble MWF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (218.07, 20.40) {Other MWF  exposure};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (126.10,  5.50) rectangle (254.90,  8.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (131.60,  5.50) rectangle (139.60, 13.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,fill=fillColor] (132.31,  6.21) rectangle (138.89, 12.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (145.10,  6.40) {Hypothetical exposure limit};
\end{scope}
\end{tikzpicture}
